---
title: "Untitled"
author: "xyz`"
date: "2023-04-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Dependency Loading:

```{r}
library(readxl)
library(tidyr)
library(tidyverse)
library(dplyr)
```


###Data Transformation Functions:

```{r}
transformations_on_excel <- function(data, bank_flag){
  df <- data.frame(data)

  df_t <- data.frame(t(df))
  colnames(df_t) <- df_t[1, ]
  df_t <- df_t[-1, ]

  df_t <- cbind(Date = rownames(df_t), df_t)
  rownames(df_t) <- 1:nrow(df_t)
  
  date_str <- df_t$Date[[1]]
  date_str_f2 <- substr(date_str, 1, 2)
  
  if (date_str_f2 == "X4"){
    dates <- as.numeric(substr(df_t$Date, 2, 6))
    Dates <- as.Date(dates, origin = '1899-12-30')
    df_t$Date <- Dates
  } else{
    dates <- sapply(df_t$Date, substr, start = 1, stop = 11)
    dates <- data.frame(dates)
    dates$Dates <- as.Date(sub("X", "", dates$dates), format = "%m.%d.%Y")
    df_t$Date <- dates$Dates
  }
  
  
  df_t <- df_t[ , !names(df_t) %in% NA]
  df_t_filtered <- df_t %>% select(-starts_with('NA'))
  
  if(bank_flag==1){
    df_t_filtered <- df_t_filtered[seq(from = 1, to = nrow(df_t_filtered), by = 3),]
  } else if(bank_flag==2){
    df_t_filtered <- df_t_filtered[seq(from = 1, to = nrow(df_t_filtered), by = 1),]
  } else if(bank_flag==0){
    df_t_filtered <- df_t_filtered[seq(from = 2, to = nrow(df_t_filtered), by = 3),]
  }
  return(df_t_filtered)
}
```


###Data Loading:

```{r}
aggregate_bank_reports <- function(bank_flag, pg_flag, sheet){
  parentdir <- dirname(normalizePath(file.path(getwd(),'.')))
  cur<-file.path(parentdir,'Data')
  
  bank1 <- read_excel(file.path(cur,'Silicon_Valley_bank.xlsx'), sheet=sheet)
  bank2 <- read_excel(file.path(cur,'Citizens_bank.xlsx'), sheet=sheet)
  bank3 <- read_excel(file.path(cur,'HSBC_bank.xlsx'), sheet=sheet)
  bank4 <- read_excel(file.path(cur,'Morgan_Stanley_bank.xlsx'), sheet=sheet)
  bank5 <- read_excel(file.path(cur,'First_Republic_bank.xlsx'), sheet=sheet)
  
  bank1_df <- transformations_on_excel(bank1, bank_flag)
  names(bank1_df)[2] <- "Bank"
  bank1_df$Bank <- "Silicon Valley Bank"
  bank2_df <- transformations_on_excel(bank2, bank_flag)
  names(bank2_df)[2] <- "Bank"
  bank2_df$Bank <- "Citizens Bank, National Association"
  bank3_df <- transformations_on_excel(bank3, bank_flag)
  names(bank3_df)[2] <- "Bank"
  bank3_df$Bank <- "HSBC Bank USA, National Association"
  bank4_df <- transformations_on_excel(bank4, bank_flag)
  names(bank4_df)[2] <- "Bank"
  bank4_df$Bank <- "Morgan Stanley Private Bank, National Association"
  bank5_df <- transformations_on_excel(bank5, bank_flag)
  names(bank5_df)[2] <- "Bank"
  bank5_df$Bank <- "First Republic Bank"
  
  if (pg_flag == 1){
    pg_df <- transformations_on_excel(bank3, 0)
    names(pg_df)[2] <- "Bank"
    pg_df$Bank <- "Relative Peer Group"
    final_bank_df <- rbind(bank1_df, bank2_df, bank3_df, bank4_df, bank5_df, pg_df)
  } else{
    final_bank_df <- rbind(bank1_df, bank2_df, bank3_df, bank4_df, bank5_df)
  }
  
  rownames(final_bank_df) <- 1:nrow(final_bank_df)
  return(final_bank_df)
}
```


```{r}
SR_data <- aggregate_bank_reports(1, 1, "Summary Ratios")
AYFC_data <- aggregate_bank_reports(1, 1, "Asset Yields and Funding Costs")
BSP_data <- aggregate_bank_reports(1, 1, "Balance Sheet Percentage")
IRR_data <- aggregate_bank_reports(1, 1, "Interest Rate Risk")
LF_data <- aggregate_bank_reports(1, 1, "Liquidity and Funding")
LF_tot_data <- aggregate_bank_reports(2, 0, "Liquidity and Funding - Totals")
LI_data <- aggregate_bank_reports(1, 1, "Liquidity & Investment")
LI_tot_data <- aggregate_bank_reports(2, 0, "Liquidity & Investment - Totals")
CAD_data <- aggregate_bank_reports(2, 0, "Capital Analysis D")

CAD_data <- CAD_data[-11,]
rownames(CAD_data) <- 1:nrow(CAD_data)
```


###Visualizations:


1) Change in Assets and Tier 1 Capital for all competitor Banks over time:

```{r}

SR_data %>% ggplot(aes(x = `Date`,y = as.numeric(`Total Assets`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) +
             labs(title = "The Annual Change in Total Assets",
                  y = "Change in Assets in %",
                  x = "Date") + 
             guides(size = FALSE) +
             theme_classic()


SR_data %>% ggplot(aes(x = `Date`,y = as.numeric(`Tier 1 Capital`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) +
             labs(title = "The Change in Tier 1 Capital",
                  y = "Change in Tier 1 Capital in %",
                  x = "Date") + 
             guides(size = FALSE) +
             theme_classic()

```




2) Customer deposits to Silicon Valley Bank over time:

```{r}

LF_tot_data %>%  ggplot(aes(x = `Date`,y = as.numeric(`Total Deposits.1`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Total deposits by Customers",
                  y = "Deposits",
                  x = "Date") +  
             guides(size = FALSE) +
             scale_y_continuous(labels = scales::comma) +
             theme_classic()
  
```



3) Division of Capital of Banks into different Asset categories:

```{r}

AYFC_data %>% ggplot(aes(x = `Date`,y = as.numeric(`Total Investment Securities`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Total Securities held by Banks", 
                  subtitle = "divided by total assets of the Bank",
                  y = "Total Securities in %",
                  x = "Date") +  
             guides(size = FALSE) +
             theme_classic()

AYFC_data %>% ggplot(aes(x = `Date`,y = as.numeric(`Total Loan & Leases`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Total Loans & Leases given out by Banks", 
                  subtitle = "divided by total assets of the Bank",
                  y = "Total Loans & Leases in %",
                  x = "Date") +  
             guides(size = FALSE) +
             theme_classic()

AYFC_data %>% ggplot(aes(x = `Date`,y = as.numeric(`Interest-Bearing Bank Balances`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Total Interest-Bearing Bank Balances", 
                  subtitle = "divided by total assets of the Bank",
                  y = "Total Interest-Bearing Bank Balances in %",
                  x = "Date") +  
             guides(size = FALSE) +
             theme_classic()


```



4) SVB clearly has an overexposure to Securities:

```{r}

IRR_data %>% ggplot(aes(x = `Date`,y = as.numeric(`Held to Maturity`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Total Held-to-Maturity Securities", 
                  subtitle = "divided by total assets of the Bank",
                  y = "Held-to-Maturity Securities in %",
                  x = "Date") +  
             guides(size = FALSE) +
             theme_classic()

IRR_data %>% ggplot(aes(x = `Date`,y = as.numeric(`Available for Sale`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Total Available for Sale Securities", 
                  subtitle = "divided by total assets of the Bank",
                  y = "Available for Sale Securities in %",
                  x = "Date") +  
             guides(size = FALSE) +
             theme_classic()

```



5) Among Held-to-Maturity Securities, they are overexposed to:

```{r}

LI_data %>% filter(Bank != "First Republic Bank") %>%
       ggplot(aes(x = `Date`,y = as.numeric(`Municipal Securities`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Total Municipal Securities", 
                  subtitle = "divided by total securities of the Bank",
                  y = "Held-to-Maturity Securities in %",
                  x = "Date") +  
             guides(size = FALSE) +
             theme_classic()

LI_data %>% ggplot(aes(x = `Date`,y = as.numeric(`US Treas & Govt Agencies`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Total US Treasury & Govt Agency Securities", 
                  subtitle = "divided by the sum of total held-to-maturity Securities of the Bank",
                  y = "US Treasury & Govt Agency Securities in %",
                  x = "Date") +  
             guides(size = FALSE) +
             theme_classic()
  
```



6) Unrealized losses from the Securities due to Interest Rate Risk:

```{r}

IRR_data %>% ggplot(aes(x = `Date`,y = as.numeric(`Unrealized Appreciation/Depreciation`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Unrealized Appreciation/Depreciation of Securities", 
                  subtitle = "divided by total assets of the Bank",
                  y = "Unrealized Gain/Loss in %",
                  x = "Date") +  
             guides(size = FALSE) +
             theme_classic()

CAD_data %>% ggplot(aes(x = `Date`,y = as.numeric(`Total Risk-Weighted Assets`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Total Risk-Weighted Assets of each bank",
                  y = "Total Risk-Weighted Assets",
                  x = "Date") +  
             guides(size = FALSE) +
             scale_y_continuous(labels = scales::comma) +
             theme_classic()
  
```



7) Assets pledged for Liquidity:

```{r}

LI_data %>%  ggplot(aes(x = `Date`,y = as.numeric(`Pledged Assets`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Assets pledged for loans",
                  y = "Assets in %",
                  x = "Date") +  
             guides(size = FALSE) +
             theme_classic()

LI_tot_data %>%  ggplot(aes(x = `Date`,y = as.numeric(`Pledged Securities`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Securities pledged for loans",
                  y = "Securities",
                  x = "Date") +  
             guides(size = FALSE) +
             scale_y_continuous(labels = scales::comma) +
             theme_classic()


LF_data %>%  ggplot(aes(x = `Date`,y = as.numeric(`Short Term Non Core Funding`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Short Term Non Core Funding",
                  subtitle =  "as a percent of Total Assets",
                  y = "Non Core Funding in %",
                  x = "Date") +  
             guides(size = FALSE) +
             theme_classic()
  
```



8)

```{r}

LI_data %>%  ggplot(aes(x = `Date`,y = as.numeric(`Municipal Securities`), color = Bank)) +
             geom_point(aes(shape = Bank, size=3)) +
             geom_line(size=1) + 
             labs(title = "Total Municipal Securities", 
                  subtitle = "divided by total securities of the Bank",
                  y = "Held-to-Maturity Securities in %",
                  x = "Date") +  
             guides(size = FALSE) +
             theme_classic()

```



